---
title: "gtsummary in quarto"
format: html
theme: superhero
execute:
  echo: false
  error: true
---

```{r message=FALSE}
library(tidyverse)
library(gtsummary)
nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd", 
               "id", "nsibs", "samp", "race_eth", "sex", "region", 
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |> 
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")),
         sex_cat = factor(sex, labels = c("Male", "Female")),
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         glasses_cat = factor(glasses, labels = c("No", "Yes"))) 
```


This is the number of people in the data
```{r}
nrow(nlsy)
```



# Customization of `tbl_summary()`

```{r}
#| label: fig-table1
#| fig-cap: "Table 1 shows the descriptive statistics"
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

```{r}
#| label: fig-table2
#| fig-cap: "Table 2 shows the descriptive statistics"
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```
@fig-table1 contains a table and @fig-table2 contains a table.


```{r}

# Error in this code was that nlsy was originally all capitalized as R is case sensitive
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

We’re using some data from the National Longitudinal Survey of Youth 1979, a cohort of American young adults aged 14-22 at enrollment in 1979. They continue to be followed to this day, and there is a wealth of publicly available data online. I’ve downloaded the answers to a survey question about whether respondents wear glasses, a scale about their eyesight with glasses, their (NLSY-assigned 😒) race/ethnicity, their sex (presumably at birth, but unclear), their family’s income in 1979, and their age at the birth of their first child.


```{r}
mean_sleep_weekend <- mean(nlsy$sleep_wknd, na.rm = TRUE)
mean_sleep_weekend
```
1. There mean number of hours was `r mean_sleep_weekend`
2. There mean number of hours was `r mean(nlsy$sleep_wknd, na.rm = TRUE)`

```{r}
median_sleep_weekend <- median(nlsy$sleep_wknd, na.rm = TRUE)
median_sleep_weekend
```
3. The median numbers of hours was `r median_sleep_weekend` participants
4. The median numbers of hours was `r mean(nlsy$sleep_wknd, na.rm = TRUE)` participants"


```{r}
#| eval: true
#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
#| output-location: slide
table1 <- tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir, sleep_wknd)) |> 
  add_overall(last = TRUE)

table1

mean_hrs_sleep <- inline_text(table1, variable = "sleep_wknd", column = "stat_0")
```

The median and IQR are `r mean_hrs_sleep`
